---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spellbook

<!-- badges: start -->
<!-- badges: end -->

*A whimsical R package of reusable incantations* ✨

The spellbook package is a personal library of functions, ggplot2 themes, and palettes that I reach for often in data analysis and visualization. Instead of re-writing code across projects, I can now summon my favorite utilities directly from this grimoire.

## Installation

You can install the development version of spellbook from [GitHub](https://github.com/) with:

``` r
devtools::install_github("colebaril/spellbook")
```

## Example

### Themes and Palettes
In the following example, `theme_parchment()` is used to alter thematic elements 
of the plot and `scale_spellbook()` is used to apply my custom colour palettes.

```{r, example_theme_palette, message = FALSE, warning = FALSE, fig.dpi = 300}
library(spellbook)
library(tidyverse)
library(palmerpenguins)
library(extrafont)


ggplot(penguins, aes(flipper_length_mm, bill_length_mm, fill = species, group = species)) +
  geom_point(shape = 21) +
  geom_smooth(aes(colour = species), se = FALSE, method = "lm") +
  scale_spellbook(name = "Species", palette = "arcane_flame", type = "d", aesthetics = "fill") +
  scale_spellbook(name = "Species", palette = "arcane_flame", type = "d", aesthetics = "colour") +
  theme_parchment() +
  labs(title = "Palmer Penguin Bill Length \nvs. Flipper Length", x = "Flipper Length (mm)", y = "Bill Length (mm)")
```

### Data Cleaning

In this example, `purify_data()` is used to standardize column names, trim white 
space, convert empty columns to true `NA`s, and flags outliers for any numeric
columns using robust means.

```{r, example_cleaning}
df <- tibble::tibble(
  "First Name" = c(" Alice ", "Bob", "", "CHARLIE", "dave", "Eve", NA, "Bob", "Bob"),
  "Last Name" = c("Smith", "Jones", "O'Neil", "Brown", "Miller", "O'Brien", "", "Jones", "Jones"),
  "Score" = c(10, 5000, 15, 20, 12, -999, 14, 5000, 5000),  
  "Enrollment Date" = c("2025-01-01", "20241215", "2025/02/01", "", NA, "01-03-2025", "2025-01-01", "2024-12-15", "2024-12-15"),
  "Grade" = c("A", "b", "C", "A", "B", "", "A", "b", "b"),
  "Comments!" = c("Good", " Excellent ", "", "Needs work", NA, "Good!", "Average", " Excellent ", " Excellent "),
  "EmptyCol" = c(NA, NA, NA, NA, NA, NA, NA, NA, NA)
)

print(df)

purify_data(df, trim_chars = TRUE, empty_to_na = TRUE, flag_outliers = TRUE)
```

