---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spellbook

<!-- badges: start -->
<!-- badges: end -->

*A whimsical R package of reusable incantations* ✨

The spellbook package is a personal library of functions, ggplot2 themes, and palettes that I reach for often in data analysis and visualization. Instead of re-writing code across projects, I can now summon my favorite utilities directly from this grimoire.

## Features

- Handy utility functions for everyday analysis 🧹

- Custom ggplot2 themes (e.g. theme_parchment) styled with personality 📜

- Color palettes and styling tools for consistent plots 🎨

- Easy to expand as new “spells” are discovered ✍️

## Installation

You can install the development version of spellbook from [GitHub](https://github.com/) with:

``` r
devtools::install_github("colebaril/spellbook")
```

## Example

```{r example, message = FALSE, warning = FALSE, fig.dpi = 300}
library(spellbook)
library(tidyverse)
library(palmerpenguins)
library(extrafont)


ggplot(penguins, aes(flipper_length_mm, bill_length_mm, fill = species, group = species)) +
  geom_point(shape = 21) +
  geom_smooth(aes(colour = species), se = FALSE, method = "lm") +
  scale_fill_viridis_d("Species") +
  scale_colour_viridis_d("Species") +
  theme_parchment() 
  # labs(title = "Counts of Sex by Year", y = "Count", x = "Sex")



```


